---
title: "Women Topic in Philosophy"
output: html_notebook
---

# 1. Introduction
"It is clearly evident that women in philosophy still struggle for the right to be" (Devine, Stewart).Eventhough women in the history of philosophy are getting more attention, many scholars argue that historians of philosophy should acknowledge the influence of long-neglected female voices. The sexist views of well-known philosophers should not ignored on purpose. For instance, Aristotle, Polato and Hegel all once had negative viewpoints on women. Aristotle saw women as subject to men. By given the text data, I want to see What are different philosophy schools' viewpoints on female? What are main topics when they discussed about women? And is Aristotle hostile to women? 


# 2. Loading and Cleaning the data
The dataset is collected from the Philosophy Data Project and is public in kaggle. It is a .csv file and include 360808 observations and 11 variables. It has over 50 texts spanning 10 major schools of philosophy. The represented schools are: Plato, Aristotle, Rationalism, Empiricism, German Idealism, Communism, Capitalism, Phenomenology, Continental Philosophy, and Analytic Philosophy.

```{r,echo=FALSE, message=FALSE}
packages.used=c("rvest", "tibble", "qdap", 
                "sentimentr", "gplots", "dplyr",
                "tm", "syuzhet", "factoextra", 
                "beeswarm", "scales", "RColorBrewer",
                "RANN", "tm", "topicmodels","readtext")

# check packages that need to be installed.
packages.needed=setdiff(packages.used, 
                        intersect(installed.packages()[,1], 
                                  packages.used))
# install additional packages
if(length(packages.needed)>0){
  install.packages(packages.needed, dependencies = TRUE)
}

# load packages
library(dplyr)
library(tidyr)
library("rvest")
library("tibble")
# You may need to run
# sudo ln -f -s $(/usr/libexec/java_home)/jre/lib/server/libjvm.dylib /usr/local/lib
# in order to load qdap
library("qdap")
library("sentimentr")
library("gplots")
library("dplyr")
library("tm")
library("syuzhet")
library("factoextra")
library("beeswarm")
library("scales")
library("RColorBrewer")
library("RANN")
library("tm")
library("topicmodels")
library("readtext")
library(forcats)
library(ggplot2)
library(beeswarm)
library(RColorBrewer)
library(dplyr)
```

```{r}
textdata <- read.csv("../data/philosophy_data.csv")
head(textdata)
```
Because in this project, we mainly focus on women topic in Philosophy; therefore, we filter texts containing female keywords. The filtered datasets contains 8598 observations, and I use this dataset to do following analysis. 

# 3. Data Processing

#### 3.1 Text Proprocessing

We select philosophy text data with female topic and to see text topics variation over different schools with emotions

```{r,echo=FALSE,warning=FALSE}
#Dataset on all schools with txt related to female
schools <- unique(textdata$school)
all_text_f <-  NULL
for (i in schools){
  subtext <- textdata[textdata$school==i, c("sentence_lowered","original_publication_date","sentence_length")]
  subtext_g <- grep("female|women|woman|womens|girl", subtext$sentence_lowered, value = TRUE)
  all_text_f <- append(all_text_f, subtext_g) 
}
length(all_text_f)
head(all_text_f)
all_text_f <- data.frame(all_text_f)
colnames(all_text_f) <- "sentence_lowered"
all_text_f_date <- merge(all_text_f, textdata, by="sentence_lowered")

all_txt <- all_text_f_date$sentence_lowered

#write.csv(all_text_f_date, "../Desktop/text_with_female_topic.csv")

#For all schools!
corpus <- iconv(all_txt, to = 'utf-8-mac')
corpus <- Corpus(VectorSource(corpus))
inspect(corpus[1:5])


#Cleaning datasets:
#Remove punctuations, lowercase, common words
corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, tolower)
#inspect(corpus[1:5])
corpus <- tm_map(corpus, removeNumbers)
#inspect(corpus[1:5])
cleanset <- tm_map(corpus, removeWords, stopwords('english'))
cleanset <- tm_map(cleanset, removeWords, c('but','the', 'also'))
cleanset <- tm_map(cleanset, removeWords, 'I')
#inspect(cleanset[1:5])
cleanset <- tm_map(cleanset, removeWords, c('the','but'))
list = c('this','thus','many','still','and','may','another','yet','these','that','…','will','the','often','many','much','when','even')
cleanset <- tm_map(cleanset, removeWords, list)
#inspect(cleanset[1:5])


cleanset <- tm_map(cleanset, gsub, pattern = 'women',replacement='woman')
cleanset <- tm_map(cleanset, gsub, pattern = 'womens',replacement='woman')
cleanset <- tm_map(cleanset, gsub, pattern = 'womans',replacement='woman')

cleanset <- tm_map(cleanset, gsub, pattern = 'feman', replacement = 'woman')
cleanset <- tm_map(cleanset, gsub, pattern = 'she',replacement='woman')
cleanset <- tm_map(cleanset, gsub, pattern = 'male',replacement='man')
cleanset <- tm_map(cleanset, gsub, pattern = 'men',replacement='man')
cleanset <- tm_map(cleanset, gsub, pattern = 'mens',replacement='man')
cleanset <- tm_map(cleanset, gsub, pattern = 'mans',replacement='man')
cleanset <- tm_map(cleanset, stemDocument)
cleanset <- tm_map(cleanset, stripWhitespace)
inspect(cleanset[1:5])

sentence.list=NULL
for(i in 1:nrow(all_text_f_date)){
  sentences=all_text_f_date$sentence_lowered[i]
  if(length(sentences)>0){
    emotions=get_nrc_sentiment(sentences)
    word.count=word_count(sentences)
    # colnames(emotions)=paste0("emo.", colnames(emotions))
    # in case the word counts are zeros?
    emotions=(1/(word.count+0.01))%*%as.matrix(emotions)
    sentence.list=rbind(sentence.list, 
                        cbind(f.df[i,-ncol(f.df)],
                              sentences=as.character(sentences), 
                              word.count,
                              emotions,
                              sent.id=1:length(sentences)
                              )
    )
  }
}


head(all_text_f_date)
```


#### 3.2 Data Analysis: Process Variables for Analysis

In the following, I want to check whether women topic in philosophy becomes more popular. Whether there is an increased empirical research on women? So I drew 3 graphs here separately analyzed the weights of each school's topic on women.
First two barcharts show that school Feminism spent lots of time exploring women social positions. This is what we expect, but besides Feminism,  Aristotle tends to have more texts related to women. In addition, in year 1949, female is a popular topic.  


```{r,echo=FALSE, message=FALSE}


par(mfrow=c(2,1))

school_sentence <- all_text_f_date%>%
  group_by(school)%>%
  summarise(num_sentence = n())%>%
  arrange(desc(num_sentence))

#Total num of sentences over all schools
school_sentence%>%
  ggplot(aes(x = school, y = num_sentence))+
  geom_bar(stat = "identity", fill="#f68060", alpha=.6, width=.4)+
  coord_flip()+
  xlab("school")+
  ylab("number of sentences")+
  theme_bw()+
  labs(title = "Number of Sentences related to women over different schools")



date_sentence$year <- as.character(date_sentence$original_publication_date)

date_sentence %>%
  ggplot( aes(x=year, y=count)) +
    geom_area(fill="#69b3a2", alpha=0.5) +
  geom_bar(stat = "identity", fill="#f68060", alpha=.6, width=.4)+
    #geom_line(color="#69b3a2") +
    ylab("Number of sentences") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title = "Number of sentences related to Women over years")



```
In addition, below graph clearly indicate different schools devote various length to the description of female. Feminism describe this field in details, and so do Plato, continental and Aristotle. 

```{r,echo=FALSE, warning=FALSE}

beeswarm(sentence_length~school, data = all_text_f_date, horizontal=TRUE,
         pch=16, col=alpha(brewer.pal(9, "Set1"), 0.6), 
         cex=0.55, cex.axis=0.8, cex.lab=0.8,
         spacing=1.2/nlevels(factor(all_text_f_date$school)),
         las=2, xlab="Number of Words in a Sentence.", ylab="",
         main="The distribution of sentence lengths related to female over different school")

```

From above three graphs, we can see that on the question of women, many phisolophers show their arguments from different perspectives. They have large conversations there. 

#### 3.3 Data Analysis: Sentiment Analysis
Sentiment analysis can help us determine whether the sentence is positive, negative or neutral. It is useful for us to gain an overview of all schools' opinions behind certain topics. So we then do sentiment analysia so that we can see how philosophers shift between different sentiments.
```{r}
head(sentence.list)

```

#### 3.4 KMeans Clustering: grouping authors emotions

```{r,echo=FALSE, message=FALSE}
set.seed(2021)

presid.summary=tbl_df(sentence.list)%>%
  #group_by(paste0(type, File))%>%
  group_by(author)%>%
  summarise(
    anger=mean(anger),
    anticipation=mean(anticipation),
    disgust=mean(disgust),
    fear=mean(fear),
    joy=mean(joy),
    sadness=mean(sadness),
    surprise=mean(surprise),
    trust=mean(trust)
    #negative=mean(negative),
    #positive=mean(positive)
  )
presid.summary=as.data.frame(presid.summary)
rownames(presid.summary)=as.character((presid.summary[,1]))
km.res=kmeans(presid.summary[,-1], iter.max=200,
              4)
fviz_cluster(km.res, 
             stand=F, repel= TRUE,
             data = presid.summary[,-1], xlab="", xaxt="n",
             show.clust.cent=FALSE)
```


From above clustering charts, we apply KMeans on dataset containing sentiment scores to split all authors. Authors will be in a group if they have similar sentiment scores. I set to split the data into 4 groups. So from above four clusters, taking the red cluster as an example: it includes all authors from school feminism: Wollstonecraft, Beauvoir and Davis, so I would say Kmeans did a good job on grouping similar authors into clusters.

# 4. Data Analysis - Topic Modeling 
## 4.1 Topic Modeling 
We first performed text mining and text basic processing, then I generate document-term matrices and run LDA. For topic modeling, I prepare a corpus of sentence snipets as follows: I remove punctuation, lowercase, common(nonsense) words, duplicate key words and blankspaces. I set to select 15 topic groups, and it is shown in the following:

Based on the most popular terms and the most salient terms for each topic, we assign a hashtag to each topic: c("temporal", "society_role", "action", "demand", "sex", "doubt", "perception", "moral", "equality", "freedom", "family_role", "virgin", "love", "desire", "ethic"). 

```{r,echo=FALSE, message=FALSE}
dtm <- DocumentTermMatrix(cleanset)
#convert rownames to filenames#convert rownames to filenames
#rownames(dtm) <- paste(corpus.list$type, corpus.list$File,
                      # corpus.list$Term, corpus.list$sent.id, sep="_")

rowTotals <- apply(dtm , 1, sum) #Find the sum of words in each Document

dtm  <- dtm[rowTotals> 0, ]
corpus.list <- corpus.list[rowTotals>0, ]

#Set parameters for Gibbs sampling
burnin <- 4000
iter <- 2000
thin <- 500
seed <-list(2003,5,63,100001,765)
nstart <- 5
best <- TRUE

#Number of topics
k <- 15
library(topicmodels)
#Run LDA using Gibbs sampling
ldaOut <-LDA(dtm, k, method="Gibbs", control=list(nstart=nstart, 
                                                 seed = seed, best=best,
                                                 burnin = burnin, iter = iter, 
                                                 thin=thin))


ldaOut.topics <- as.matrix(topics(ldaOut))
table(c(1:k, ldaOut.topics))
topicProbabilities <- as.data.frame(ldaOut@gamma)

```


```{r,echo=FALSE, message=FALSE}
#Analysing topics from all schools
terms.beta=ldaOut@beta
terms.beta=scale(terms.beta)
topics.terms=NULL
for(i in 1:k){
  topics.terms=rbind(topics.terms, ldaOut@terms[order(terms.beta[i,], decreasing = TRUE)[1:7]])
}

```


```{r, echo=FALSE, warning=FALSE}
topics.terms
```

```{r}
ldaOut.terms

```

Here, I manually assign a hashtag to each topic. It is objective and might not be accurately correct. 

```{r,echo=FALSE, message=FALSE}
topics.hash=c("temporal", "society_role", "action", "demand", "sex", "doubt", "perception", "moral", "equality", "freedom", "family_role", "virgin", "love", "desire", "ethic")
corpus.list$ldatopic=as.vector(ldaOut.topics)
corpus.list$ldahash=topics.hash[ldaOut.topics]

colnames(topicProbabilities)=topics.hash

corpus.list <- data.frame(text=sapply(corpus.list, identity), 
    stringsAsFactors=F)

femaile_all_t <- all_text_f_date[, c("title","author","school","original_publication_date","sentence_length","sentence_lowered")]
corpus.list.df <- cbind(femaile_all_t, topicProbabilities)
#head(corpus.list.df)

```

## 4.2 Clustering of topics
Below the heat map shows the correlationmatrix between each school with 6 hashtags of topics. 
```{r,echo=FALSE, message=FALSE}
library(gplots)

topic.summary=tbl_df(corpus.list.df)%>%
              select(school, temporal:ethic)%>%
              group_by(school)%>%
              summarise_each(funs(mean))

topic.summary=as.data.frame(topic.summary)
rownames(topic.summary)=topic.summary[,1]
#rownames(topic.summary) <- make.names(topic.summary[,1], unique=TRUE)

topic.plot=c(2, 6, 8, 9, 11, 13)

```



```{r,echo=FALSE, message=FALSE,fig.width = 3, fig.height = 3}
heatmap.2(as.matrix(topic.summary[,topic.plot+1]), 
          scale = "column", key=F, 
          col = bluered(100),
          cexRow = 0.9, cexCol = 0.9, margins = c(8, 8),
          trace = "none", density.info = "none")


```

Above heat map shows that Aristotle has negative correlation with equality and some positive relationship with women's social positions at that time(key words in society_role class are suffer, outside, workers, labors and so on); also some external reviewers mentioned that Aristotle believed women were inferior to men. Towards the issue of Aristotle's sexist views, I want to dig more on Aristotle's attitudes on female  based on the given text data, and stand from data perspective to see Aristotle's views on women.

# 5. Aristotle's views on Women

## 5.1 Is Aristotle hostile to women?

I then select emotionally charged sentences from Aristotle. Here are some examples: 
Aristotle school use words like evil, affliction, pain and confusion to describe women.These are all negative words.

``` {r,echo=FALSE, message=FALSE}
#For school Aristotle 
print("aristotle ")
A.df=tbl_df(sentence.list)%>%
  filter(school=="aristotle",  word.count>=4)%>%
  select(sentence_lowered, anger:trust)
A.df=as.data.frame(A.df)
```

```{r}

as.character(A.df$sentence_lowered[apply(A.df[,-1], 2, which.max)])

```


## 5.2 Comparing Aristotle's sentences to Feminism's
In order to more objectively see whether Aristotle has bias on female, I also select emotional changed sentences from school feminism. While school feminism used words like sweet, humble to reflect girls. By comparison, we can clearly see that Aristotle underestimate woman's role in the society. 

```{r,echo=FALSE, message=FALSE}

#move on
print("feminism ")
f.df=tbl_df(sentence.list)%>%
  filter(school=="feminism",  word.count>=4)%>%
  select(sentence_lowered, anger:trust)
f.df=as.data.frame(f.df)

```

```{r}
as.character(f.df$sentence_lowered[apply(f.df[,-1], 2, which.max)])

```


Furthermore, I am interested in what are high frequency words that Aristotle school mostly used to describe a woman. So then I perform sentiment analysis and drew a wordcloud to intuitively see those keywords. 

#Sentiment Analysis
```{r,echo=FALSE, message=FALSE}
library(syuzhet)
library(lubridate)
library(ggplot2)
library(scales)
library(reshape2)
library(dplyr)
```


```{r,echo=FALSE, message=FALSE}
##select Aristotle group text related to female/women
AP_text <- textdata[textdata$school=="aristotle",'sentence_lowered']
AP <- grepl("female|girl|womens|women|she|feman", AP_text)
AP_text <- AP_text[AP]
#length(AP_text)
#head(AP_text)
#cleaning the dataset
corpus_AP <- iconv(AP_text, to = 'utf-8-mac')
corpus_AP <- Corpus(VectorSource(corpus_AP))

corpus_AP <- tm_map(corpus_AP, tolower)
corpus_AP <- tm_map(corpus_AP, removePunctuation)
corpus_AP <- tm_map(corpus_AP, removeNumbers)
corpus_AP <- tm_map(corpus_AP, removeWords, stopwords('english'))
corpus_AP <- tm_map(corpus_AP, removeWords, 'I')
inspect(corpus_AP[1:5])
corpus_AP <- tm_map(corpus_AP, removeWords, 'the')
corpus_AP <- tm_map(corpus_AP, removeWords, 'but')

corpus_AP <- tm_map(corpus_AP, removeWords, "one")
corpus_AP <- tm_map(corpus_AP, removeWords, "also")
corpus_AP <- tm_map(corpus_AP, removeWords, "will")
corpus_AP <- tm_map(corpus_AP, removeWords, "just")

corpus_AP <- tm_map(corpus_AP, removeWords, c('women','female','womens','woman','she','womans','femans','girls'))
#inspect(corpus_AP[1:5])
corpus_AP <- tm_map(corpus_AP, gsub, pattern = 'men',replacement = 'man')
corpus_AP <- tm_map(corpus_AP, gsub, pattern = 'male', replacement = 'man')
corpus_AP <- tm_map(corpus_AP, gsub, pattern = 'boy', replacement = 'man')
corpus_AP <- tm_map(corpus_AP, gsub, pattern = 'mans', replacement = 'man')

corpus_AP <- tm_map(corpus_AP, removeWords, "man")
corpus_AP <- tm_map(corpus_AP, removeWords, c("another", "either", "sometimes", "always"))
clean_AP <- tm_map(corpus_AP, stripWhitespace)

#inspect(clean_AP[1:5])
```




```{r, warning=FALSE,fig.width = 3, fig.height = 3}
#Wordcloud(freq used words) for Aristotle
set.seed(2021)

tmd_AP <- TermDocumentMatrix(clean_AP)
tmd_AP <- as.matrix(tmd_AP)
w_AP <- sort(rowSums(tmd_AP), decreasing = TRUE)

AP_freq_w <- subset(w_AP, w_AP>=20)

wordcloud(words = names(AP_freq_w),
          freq = AP_freq_w,
          colors = brewer.pal(10, 'Dark2'),
          scale = c(8,0.3))
```

The word cloud shows additional words that occur frequently and could be of interest for further analysis. From above word cloud, we can see that keywords such as like, must, eggs, first are frequently used by school Aristotle when they talked about women. The top twenty words include animals, organ, seman, distinguished and so on. They words could provide more context around the most frequently occurring words and help to gain a better understanding of the main themes. These words reflect Aristotle's gender bias view on female that women as subject to men.From these words, we rarely see positive image of women. Below is an example of Aristotle's sentence with keyword organ:

```{r}
test_A <- grepl("organ|seman", AP_text)
AP_text <- AP_text[test_A]
AP_text[7]
```

From this example, we can see that for Aristotle, women's purpose is to give birth to children. His opinion is biased and not acceptable in today's world. 


```{r}
#Sentiment bar chart
#obtain sentiment score
fel_text <- iconv(clean_AP, to = 'utf-8-mac')

s <- get_nrc_sentiment(fel_text)


barplot(colSums(s),
        las = 2,
        col = 'blue',
        ylab = 'Count')
```

The bar plot shows the count of words in the text, associated with each emotion. Negative emotions in Aristotle's text appear more oftern.
This bar chart demonstrates that words associated with the negative emotion occurred about six hundred times in the text, whereas words associated with the positive emotion of “surprise” occurred less than 200 times.From sentiment bar chart, it reflects emotions classification, we could see that besides  two highest bars of negative and positive, most school Aristotle's sentences contain words which have sentiments such as fear, sadness and trust.



# 6. Conclusion
All in all, based on the analysis, we can see that there has been increased empirical research on women’s underrepresentation in philosophy at various levels; however, there is a clear pattern that women are unequally in philosophy school Aristotle. At year 1949, Feminist philosophy has become mainstream, and school Feminism bring attention to women: What are women's role" and discussed gender of roles and responsibilities. 



# 7. Issues and Potential Biases
There are issues on sentiment analysis. Since there are ambiguous words used to describe authors' perspectives on gender roles; for example: "Conversely, if men in general are taller than women, then the tallest man is taller than the tallest woman." It is clearly that Aristotle thought women are not equal to men and female are inferior; however, words he used are taller, tallest and than, so sentiment analysis thinks of this sentence with emotions trust, positive. That is totally opposite of Aristotle's view, so sentiment analysis has some limitations on philosophy text data, and for further study, we might need to manually go through each text and label them. 

```{r}
textdata[textdata$sentence_spacy=="Conversely, if men in general are taller than women, then the tallest man is taller than the tallest woman.",  ]
```
```{r}
get_nrc_sentiment("Conversely, if men in general are taller than women, then the tallest man is taller than the tallest woman.")
```


### Source
+ [Justin Weinberg, How What It Is Like to Be a Woman in Philosophy has Changed over the Past Decade]( https://dailynous.com/2021/06/04/how-what-it-is-like-to-be-a-women-in-philosophy-has-changed-over-the-past-decade/)
+ [Nesta Devine,  Georgina Stewart, Women, philosophy, and education](https://www.tandfonline.com/doi/full/10.1080/00131857.2018.1493420)




